Quantum Hoare Types

### 2019-09-27 paper/paper.tex
Add Silq (pretty close lang design to what I was thinking)
Normalize used citations

Previous work such as Proto-Quipper\cite{2015arXiv151002198R} and QWire\cite{rand18,paykin18} utilize a linear type system and dependent types to enforce a small subset of semantic properties in the quantum setting such as the no-cloning theorem and whether a unitary operator is of the right dimension. These advances in quantum type systems although helpful, still fall short in encoding and enforcing even more useful properties that one would like to be able to express for the purpose of verification. Inspired by the use of Hoare triples in the verification of imperative programs and building on the idea of Hoare Types in classical programming languages, we propose Quantum Hoare Types aimed at enabling both sound static type checking and formal verification of quantum programs.

@@

Recent work at Princeton as part of EPiQC\footnote{EPiQC: Enabling Practical-Scale Quantum Computation:  \url{https://epiqc.cs.uchicago.edu}}\cite{DBLP:conf/oopsla/HuangM18,Huang:2019:SAV:3307650.3322213} has identified several classes of bugs in quantum programs and proposed approaches to tackle them. They proposed assertion checking using preconditions and post-conditions as one of the most effective techniques for most such classes of bugs.

@@

\cite{DBLP:conf/oopsla/HuangM18}

\cite{Huang:2019:SAV:3307650.3322213}

\cite{nanevski_morrisett_birkedal_2008}

\cite{paykin18}

\cite{rand18}

\cite{2015arXiv151002198R}

\cite{PGL-045}

>>>>

Previous work such as Proto-Quipper\cite{ross2015algebraic} and QWire\cite{paykin2018,rand2018a} utilize a linear type system and dependent types to enforce a small subset of semantic properties in the quantum setting such as the no-cloning theorem and whether a unitary operator is of the right dimension. These advances in quantum type systems although helpful, still fall short in encoding and enforcing even more useful properties that one would like to be able to express for the purpose of verification. Inspired by the use of Hoare triples in the verification of imperative programs and building on the idea of Hoare Types in classical programming languages, we propose Quantum Hoare Types aimed at enabling both sound static type checking and formal verification of quantum programs.

@@

Recent work at Princeton as part of EPiQC\footnote{EPiQC: Enabling Practical-Scale Quantum Computation:  \url{https://epiqc.cs.uchicago.edu}}\cite{huang2018,huang2019} has identified several classes of bugs in quantum programs and proposed approaches to tackle them. They proposed assertion checking using preconditions and post-conditions as one of the most effective techniques for most such classes of bugs.

@@

\cite{huang2018}

\cite{huang2019}

\cite{nanevski2008}

\cite{paykin2018}

\cite{rand2018a}

\cite{ross2015algebraic}

\cite{ringer2019}

\cite{silq}
